Single-molecule Förster Resonance Energy Transfer (smFRET) allows
probing intermolecular interactions and conformational changes in
biomacromolecules, and represents an invaluable tool for studying
cellular processes at the molecular scale. smFRET experiments can
detect the distance between two fluorescent labels (donor and acceptor)
in the 3-10~nm range. In the commonly employed confocal geometry,
molecules are free to diffuse in solution. When a molecule traverses
the excitation volume, it emits a burst of photons, which can be detected
by single-photon avalanche diode (SPAD) detectors. The intensities of
donor and acceptor fluorescence can then be related to the distance
between the two fluorophores.

While in recent years we observed a growing number of contributions
proposing improvements or new techniques in smFRET data analysis,
rarely those publications were accompanied by a software implementation.
Remarkably, given the widespread application of smFRET, no complete
software package for smFRET burst analysis is freely available to date.

In this paper, we introduce FRETBursts, an open source software
for analysis of freely-diffusing smFRET data.
Fundamental steps in the analysis involve identifying photon bursts
from single molecules in a continuous stream of photons, estimating
background and other correction factors, filtering bursts and extracting
the corrected FRET efficiencies for each sub-population.
FRETBursts allows executing all these steps using both state-of-the-art
algorithms and improved techniques.
FRETBursts provides an open, robust and well-documented
implementation for commonly employed algorithms and represents
an ideal platform for comparison and development of new methods
in burst analysis.

We employed modern software engineering best-practices in order to
minimize the chance of bugs and facilitate long-term maintainability.
Furthermore, we place a strong focus on reproducibility by relying on
Jupyter notebooks for the execution of FRETBursts workflows.
Notebooks are executable documents capturing all the steps of the
analysis (including data files, input parameters, and results) and can
be easily shared to replicate complete FRETBursts workflows.
This execution model allows beginners to execute complex workflows
and advanced users to customize the analysis for their own need.
By standardizing both execution and description of the analysis by
using Jupyter notebooks, FRETBursts enables the single-molecule
community to seamless share and report reproducible workflows of
smFRET analyses.
