\subsection{Burst search}
\label{sec:burstsearch}

\subsubsection{Introduction to burst search}
\label{sec:burstsearch_intro}

After background estimation, the burst search is the next fundamental step of
the analysis. The core "sliding window" algorithm, proposed by
Eggeling~\textit{et al.} in 1998~\cite{Eggeling_1998}, involves searching for
bursts of photons
in which $m$ consecutive photons are contained within a minimal time period
$\Delta t$. In other words, bursts are portions of the photon stream where the
local rate (computed using $m$ photons) is above a minimal rate chosen as a
threshold. Eggeling did not provide any criteria on how to choose the rate
threshold and the number of photons $m$ and as therefore it has become a common
practice to manually tweak those parameters for each specific measurement. 

A more general approach consists in taking into account the background rate of
the specific measurements and in choosing a rate threshold that is $F$ times
larger than the background rate. This approach assures that all the resulting bursts
have a Signal-To-Background ratio (SBR) larger than
$(F-1)$~\cite{Michalet_2012}. A consistent criterion for choosing the threshold is
very important when comparing different measurements with different background
rates, when the background significantly varies during measurements or in
multi-spot measurements where each spot has a different background rate.

A second important aspect of burst search is which photon stream is processed.
In some cases, for instance when identifying FRET populations, one would like to
apply the burst search to all the photons. Other times, when focusing on
donor-only or acceptor only populations, it is better to use only the donor or
acceptor signal. In general one would like to be able to apply the burst search
to an arbitrary selection of photons. In FRETBursts this can be achieved by passing
the appropriate \verb|Ph_sel| object to the burst search method (see
section~\ref{sec:ph_streams} for more info on photon stream definitions).

Finally, Nir~\textit{et al.}~\cite{Nir_2006} proposed a Dual-Channel Burst
Search (DCBS) that can help mitigating artifacts due to
photo-physical effects such as photo-blinking. In this case a search is performed
independently on two photon streams and bursts are marked only when both photon
streams exhibit a rate higher than the threshold, 
implementing a kind of an AND-gate logic. 
Usually, the term DCBS refers to a burst search where the two photon streams
are (1) all the photons 
during donor excitation (\verb|Ph_sel(Dex='DAem')|) and (2) acceptor channel photons
during acceptor 
excitation (\verb|Ph_sel(Aex='Aem')|).

After each burst search it is important to select
bursts according to their number of photons (burst size). In the most
basic form, this selection can be performed during burst search by discarding
bursts with size smaller than a threshold $L$, as originally proposed by 
Eggeling~\textit{et al.}~\cite{Eggeling_1998}. 
This method, however, neglects the effect
of background and gamma factor on the burst size and can lead to a selection
bias of certain channels and/or sub-populations. 
For this reason we advocate performing a burst size selection after background
correction and taking into account the gamma factor, as illustrated in
section~\ref{sec:burstsel}.

\subsubsection{Burst search in FRETBursts}
\label{sec:burstsearch_code}

In FRETBursts the standard burst search is performed calling the
\href{http://fretbursts.readthedocs.org/en/latest/data\_class.html#fretbursts.burstlib.Data.burst\_search}{\texttt{burst\_search} method}.

\begin{verbatim}
d.burst_search(F=6, m=10, ph_sel=Ph_sel('all'))
\end{verbatim}

The previous command performs a burst search on all photons
(\verb|ph_sel=Ph_sel('all')|), with a minimum rate 6 times larger than the
background rate (\verb|F=6|) and using 10 consecutive photons to compute the
local rate (\verb|m=10|).
A different photon selection, threshold ($F$) or number of photons for rate
computation $m$ can be selected by passing a different value. These parameters
are generally a good starting point for smFRET analysis but can be tweaked in
specific cases.

Note that, in the previous burst search, no burst size selection is performed
(i.e. the minimum bursts size is $m$). 
An additional parameter $L$ can be passed to apply a threshold on the raw burst
size (before any correction). 
We, however, strongly encourage performing an more accurate burst size selection as shown in
the next section~\ref{sec:burstsel}.

In µs-ALEX there are 3 important correction parameters: gamma factor, donor spectral
leakage into the acceptor channel and acceptor direct excitation~\cite{Lee_2005}. 
These corrections can be applied by simply setting the respective \textit{Data} attributes:

\begin{verbatim}
d.gamma = 0.85
d.leakage = 0.04
d.dir_ex = 0.08
\end{verbatim}

These attributes can be assigned either before or after the burst search. In the
latter case, the burst data is
automatically updated using the newly assigned correction values.

Sometimes it may be useful to specify a fixed threshold, instead 
of a threshold derived from the background rate like in the previous example. In
this case, instead of $F$ we can use the argument \verb|min_rate_cps| that
specifies a threshold in Hertz. For example, a burst search with a 50~kHz
threshold can be performed as follows:

\begin{verbatim}
d.burst_search(min_rate_cps=50e3, m=10, ph_sel=Ph_sel('all'))
\end{verbatim}

Finally, to perform a DCBS burst search (or in general an AND-gate burst search,
see section~\ref{sec:burstsearch_intro}) the plugin function 
\href{http://fretbursts.readthedocs.org/en/latest/plugins.html#fretbursts.burstlib\_ext.burst\_search\_and\_gate}{\texttt{burst\_search\_and\_gate}}
can be used like in the following example:

\begin{verbatim}
d_dcbs = bext.burst_search_and_gate(d, F=6, m=10)
\end{verbatim}

Note that in this case a copy of the \verb|Data| variable is returned (here called \verb|d_dcbp|)
containing the results of the new burst search. In order to
save RAM, FRETBursts shares the read-only arrays timestamps and detectors between
different copies of a \verb|Data| object (for example \verb|d| and
\verb|d_dcbs|), while all the other data (including background and burst data)
is copied. 

The function \verb|burst_search_and_gate| provides additional arguments
\verb|ph_sel1| and \verb|ph_sel2| whose defaults values correspond to the 
classical DCBS photon stream selection (see section~\ref{sec:burstsearch_intro}).
These arguments can be specified to select different photon streams than in 
a classical DCBS.
