\section{Conclusions}
\label{sec:conclusions}

FRETBursts is an open source and openly developed (see SI~\ref{sec:dev}) implementation
of established smFRET burst analysis methods
made available to the single-molecule community.
It implements several novel concepts which improve the analysis results, such as
time-dependent background estimation, background-dependent burst search threshold,
burst weighting and $\gamma$-corrected burst size selection.
More importantly, FRETBursts provides a library of thoroughly-tested functions
for timestamps and burst manipulation, making it an ideal platform for
developing and comparing new analytical techniques.

We envision FRETBursts both as a state-of-the-art burst analysis
software as well as a platform for development and assessment of novel algorithms.
To underpin this envisioned role, FRETBursts is developed following modern
software engineering practices, such as DRY principle
(\href{http://en.wikipedia.org/wiki/Don\%27t_repeat_yourself}{link})
to reduce duplication and KISS principle
(\href{http://en.wikipedia.org/wiki/KISS_principle}{link})
to reduce over-engineering. Furthermore, to minimize the number software errors~\cite{Merali_2010,Soergel_2015},
we employ defensive programming~\cite{Prli__2012} which includes code readability,
unit and regression testing and continuous integration~\cite{Eglen_2016}.
Finally, being open source, any scientist can inspect the source code,
fix errors, adapt it to her own needs.

We believe that, in the single-molecule community,
standard open source software implementations, such as FRETBursts, can enhance
reliability and reproducibility of analysis and promote a faster adoption of novel methods,
while reducing the duplication of efforts among different groups.

\section*{Acknowledgments}
We thank Dr. Eyal Nir and Dr. Toma Tomov for support in the implementation of the 2CDE method and Dr. Achillefs Kapanidis and Dr. Nicole Robb for providing 
experimental data for testing the BVA implementation.
This work was supported by National Institutes of Health (NIH)
grant R01-GM95904 and R01-GM069709. Dr. Weiss discloses equity in
Nesher Technologies and intellectual property used in the research
reported here. The work at UCLA was conducted in Dr. Weiss’s Laboratory. 
