\subsection{Development and Contributions}
\label{sec:dev}
Errors are an inevitable reality in any reasonably complex 
software~\cite{Merali_2010,Soergel_2015}. It is
therefore critical to implement countermeasures to
minimize the probability of introducing bugs and their potential 
impact~\cite{Prli__2012, Wilson_2014}.
In developing FRETBursts we leverage open source technlogies
and follow modern software development best-practices as summarized below.

FRETBursts (and the entire python ecosystem it depends on) is open source
and the source code is fully available for any scientist to study,
review and modify.
The open source nature of FRETBursts and of the python ecosystem,
not only makes it a more transparent, reviewable platform
for scientific data analysis, but also allows
to leverage state-of-the-art online services such as GitHub (\href{http://https://github.com}{link}) for hosting,
issues tracking and code reviews, TravisCI
(\href{https://travis-ci.org}{link}) and AppVeyor (\href{http://www.appveyor.com/}{link}) for continuous integration
(i.e. automated test suite execution on multiple platforms after each commit)
and \href{https://readthedocs.org/}{ReadTheDocs.org} for automatic documentation 
building and hosting.
All these services would be extremely costly, if available at all,
for a proprietary software or platform~\cite{Freeman_2015}.

We highly value source code readability, a property which can
reduce the number of bugs by facilitating understanding and verifying the code.
For this purpose, FRETBursts code-base is well commented (with comments 
representing over 35\% of the source code),
follows the PEP8 python code style rules 
(\href{https://www.python.org/dev/peps/pep-0008/}{link}),
and has docstrings in napoleon format 
(\href{http://sphinxcontrib-napoleon.readthedocs.org/}{link}).

Reference documentation is built with Sphinx (\href{http://sphinx-doc.org/}{sphinx-doc.org})
and all API documents are automatically generated from docstrings.
On each commit, documentation is automatically built and deployed on
\href{https://readthedocs.org/}{ReadTheDocs.org}.

Unit tests cover most of the core algorithms, ensuring consistency and
minimizing the probability of introducing bugs.
The continuous integration services, execute the full test suite 
on each commit on multiple platforms, immediately reporting errors.
As a rule, whenever a bug is discovered, the  fix also includes a new test
to ensure that the same bug does not happen in the future.
In addition to the unit tests, we include a regression-test notebook
(\href{https://github.com/tritemio/FRETBursts/blob/master/notebooks/dev/tests/FRETBursts%20-%20Regression%20tests.ipynb}{link})
to easily compares numerical results between two versions of FRETBursts.
Additionally, the tutorials themselves are executed before each release as
an additional test layer to ensure that no errors or regressions are introduced.

FRETBursts is openly developed using the GitHub platform.
The authors encourage users to use GitHub issues for questions, discussions
and bug reports, and to submit patches through GitHub pull requests.
Contributors of any level of expertise are welcome in the projects
and publicly acknowledged.
Contributions can be as simple as pointing out deficiencies in the
documentation but can also be bug reports or corrections to
the documentation or code. Users willing to implement
new features are encouraged to open an Issue on GitHub and to submit
a Pull Request. The open source nature of FRETBursts guarantees that
contributions will become available to the entire single-molecule
community.
